\documentclass[final,letterpaper,12pt]{article}
% if you use "report", you get a separate title page
%\documentclass[final,letterpaper,twoside,12pt]{report}
%

\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{float}
\usepackage{url}
%\usepackage(hyperref}
%
% set the version number
%
\newtoks\versionnumber
\versionnumber ={1\_0}



\author{John~Wooten~Ph.D.\\
}
\date{\today \\
%br\input{rights}
}
\title{EngagemoreCRM Software Technical Report		}
\makeindex
\restylefloat{figure}

\begin{document}
\maketitle

\begin {abstract}
\noindent The technical description of a database and web application
for tracking and managing EngagemoreCRM customers and their payments.
The Thrivecart application is used to allow customers to sign up for various
subscription options.  Their signups result in a webhook notification being sent to
the thrivecart.php webhook.  This processes their action and creates or modifies
the customers EngagemoreCRM account.
\end{abstract}
\newpage
\tableofcontents
\newpage
\listoffigures
\listoftables

\newpage
\section{Track Changes}
\begin{table}[h]
\begin{center}
\begin{tabular}{|c|c|l|c|} \hline
$ Date $ & $Editor$ & $Comment$ & $Version$ \\
\hline
191125 & J. Wooten & Initial Draft & 0.1  \\

\hline
\end{tabular}
\end{center}
\caption {Table of Changes}
\label{tab:cqdata0}
\end{table}

\newpage
\section{Introduction}
\noindent Customers who desire to utilize the EngagemoreCRM services, are directed
to a Thrivecart site where they enter their subscription information, which Thrivecart manages.
Upon completion of their signup, a webhook notication is sent to the webhook 'thrivecart.php' on
a server used by EngagemoreCRM.  That webhook, updates the customer information stored in a mysql
database called user-db/users, which keeps the thrivecartID and after adding the user to EngagemoreCRM,
the engagemoreId and the status.  A web-app is available to examine the users database table, and also
the the logs database table. The logs database table contains the logs of each transaction received
from Thrivecart.


\section{Approach}
\noindent In order to process thrivecart events that are related to EngagemoreCRM users, we must connect
the thrivecardid which is sent by Thrivecart when a user is added to the resulting EngagemoreCRM id that
occurs when a new user is created within EngagemoreCRM.  This allows us to manage future Thrivecart
notifications about cancellation of their subscription and possible upgrades in their subscription.

\section{Database Tables}
\noindent There are two database tables, users, and logs that are used by the webhook.  Their structures are:
\smallskip
\begin{table}[ht]
\begin{tabular}{|l|l|l|l|l|}
\hline
Name&Type&Null&Default&Extra\\ \hline
id&int(11)&No&None&Auto Increment\\
added&datetime&No&None&\\
email&varchar(128)&No&None&\\
thrivecartid&varchar(64)&No&None&\\
engagemoreid&varchar(64)&No&None&\\
status&varchar(256)&No&None&\\
\hline
\end{tabular}
\caption{\label{tab:users}users table.}
\end{table}
\newpage
\noindent and:
\begin{table}[ht]
\begin{tabular}{|l|l|l|l|l|}
\hline
Name&Type&Null&Default&Extra\\ \hline
id&int(11)&No&None&AutoIncrement\\
received&datetime&No&None&\\
email&varchar(128)&No&None&\\
request\_json&varchar(16000)&No&None&\\
status&varchar(128)&No&None&\\
\hline
\end{tabular}
\caption{\label{tab:logs}logs table.}
\end{table}
\end{document}
